Honey Bee Colonies Impacted by Varroa, American Foulbrood and Global Warming

### 2024-08-01 starter-analysis-exercise/products/report/manuscript_final-2.qmd
HTML7 Picture adjustments

Honeybees have served as nature's pollinators for centuries. With their
relationship with humans documented as far back as ancient Egyptian and
Hindu cultures. Historically, humans have maintained beehives and
utilized honey for its medicinal properties in various civilizations,
including the Egyptians, Assyrians, Chinese, Greeks, and Romans. Honey's
natural antibacterial qualities made it a valuable treatment for wounds.
This was a practice continued by Romans and Russians during World War I.
Honeybees and other pollinators are essential for food production and
nutritional security. But even though they face numerous survival
challenges Varroa mites pose a significant threat to bee colonies. These
tiny red-brown parasites live on adult honeybees and reproduce on larvae
and pupae. Another major threat is American Foulbrood Disease (AFB).
This is caused by the bacterium Paenibacillus larvae, which is fatal to
honeybee larvae and requires incineration of infected hives to prevent
its spread. The impact of climate change on honeybee colony losses is a
growing area of research. While correlations have been found between
higher winter temperatures and increased colony losses, the effects of
warmer autumn and winter temperatures on colony dynamics and survival
require further investigation. ***Dennis and Kemp's study on honey bee
hive collapse [@hivecollapse] provides important insights into Allee
effects and ecological resilience.***[@usda_honey_bees; @usda_nass]***
***Warmer climate may impact bees[@2024warmer]***

@@

***[@varroamap] Varroa Map of infestation periods***

@@

Bee colonies maintained by beekeepers are considered livestock by the
USDA due to their ability to produce honey, a consumable food item, and
their essential role in assisting farmers with pollination crop seasons.
Given the importance of bee colonies in agriculture, it was logical to
source data from the following two authoritative websites: 1. USDA
National Agricultural Statistics Service (NASS): This site provides
comprehensive agricultural data, including statistics on honey
production and colony health. 2. Bee Informed Partnership: This site
offers detailed insights and research on bee colony management and
health, contributing valuable information on the status and trends of
bee populations. Index Catalog // USDA Economics, Statistics and Market
Information System. (n.d.-a).
https://usda.library.cornell.edu/catalog?f%5Bkeywords_sim%5D%5B%5D=honey+bees&locale=en\
USDA - National Agricultural Statistics Service - Surveys - honey bee
surveys and reports. (n.d.).
https://www.nass.usda.gov/Surveys/Guide_to_NASS_Surveys/Bee_and_Honey/

@@

![](/images/Bee%20Feeding.jpg){fig-align="center"}

>>>>

Honeybees have served as nature's pollinators for centuries. With their
relationship with humans documented as far back as ancient Egyptian and
Hindu cultures. Historically, humans have maintained beehives and
utilized honey for its medicinal properties in various civilizations,
including the Egyptians, Assyrians, Chinese, Greeks, and Romans. Honey's
natural antibacterial qualities made it a valuable treatment for wounds.
This was a practice continued by Romans and Russians during World War I.
Honeybees and other pollinators are essential for food production and
nutritional security. But even though they face numerous survival
challenges Varroa mites pose a significant threat to bee colonies. These
tiny red-brown parasites live on adult honeybees and reproduce on larvae
and pupae. Another major threat is American Foulbrood Disease (AFB).
This is caused by the bacterium Paenibacillus larvae, which is fatal to
honeybee larvae and requires incineration of infected hives to prevent
its spread. The impact of climate change on honeybee colony losses is a
growing area of research. While correlations have been found between
higher winter temperatures and increased colony losses, the effects of
warmer autumn and winter temperatures on colony dynamics and survival
require further investigation. ***Dennis and Kemp's study on honey bee
hive collapse [@hivecollapse] provides important insights into Allee
effects and ecological resilience.*** [@usda_honey_bees;
@usda_nass]\*\*\*

***Warmer climate may impact bees[@2024warmer]***

@@

[@varroamap] ***Varroa Map of infestation periods***

@@

Bee colonies maintained by beekeepers are considered livestock by the
USDA due to their ability to produce honey, a consumable food item, and
their essential role in assisting farmers with pollination crop seasons.
Given the importance of bee colonies in agriculture, it was logical to
source data from the following two authoritative websites: 1. USDA
National Agricultural Statistics Service (NASS): This site provides
comprehensive agricultural data, including statistics on honey
production and colony health. 2. Bee Informed Partnership: This site
offers detailed insights and research on bee colony management and
health, contributing valuable information on the status and trends of
bee populations. [@usda_honey_bees]

Index Catalog // USDA Economics, Statistics and Market Information
System. (n.d.-a).
https://usda.library.cornell.edu/catalog?f%5Bkeywords_sim%5D%5B%5D=honey+bees&locale=en\
USDA - National Agricultural Statistics Service - Surveys - honey bee
surveys and reports. (n.d.).
https://www.nass.usda.gov/Surveys/Guide_to_NASS_Surveys/Bee_and_Honey/

@@

![](/images/Bee%20Feeding.jpg){fig-align="center" width="313"}
